R for Clinical Study Reports and Submission

### 2021-11-10 index.Rmd

```{r, include = FALSE}
library(bslib)
library(xml2)
library(downlit)
library(haven)
library(dplyr)
library(tidyr)
library(r2rtf)
library(knitr)
library(kableExtra)
library(pkglite)
```

@@

**This is the work-in-progress draft of the book.**

## Authors and contributors {-}

```{r, echo = FALSE}
contributors <- c(
  person("Yilong", "Zhang", email = "yilong.zhang@merck.com", role = "aut"),
  person("Nan", "Xiao", role = "aut"),
  person("Keaven", "Anderson", role = "aut"),
  person("Yujie", "Zhao", role = "ctr"),
  person("Aiming", "Yang", role = "ctr"),
  person("Steven", "Haesendonckx", role = "ctr"),
  person("Howard", "Baek", role = "ctr")
)
```

The document is maintained by a community.
While reading the document, you can be a contributor as well.
The quality of this document relies on you.

- Author: contribute the majority content of at least one chapter.
- Contributor: [contribute at least one commit to the source code](https://github.com/elong0527/r4csr)

```{r, echo = FALSE, eval = TRUE}
data.frame(contributors = as.character(contributors)) %>%
  kable(format = "html") %>%
  kable_styling()
```

>>>>

```{r, include = FALSE}
library(bslib)
library(xml2)
library(downlit)
library(haven)
library(dplyr)
library(tidyr)
library(r2rtf)
library(knitr)
library(pkglite)
```

@@

**This is a work-in-progress draft.**

## License {-}

This book is licensed to you under [Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 International License](https://creativecommons.org/licenses/by-nc-nd/4.0/).
